PDBF Documentation

### 2015-07-22 Documentation.tex
implemented dataTables and fixed some minor bugs

\documentclass[11pt]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{PDBF}
\usepackage{wrapfig}
\usepackage[hidelinks]{hyperref}
\usepackage[a4paper,vmargin={20mm,40mm},hmargin={20mm,20mm}]{geometry}

@@

\section{Requirements}
These \LaTeX\relax packages are required for PDBF documents:\\
zref\\
xcolor\\
graphicx\\
xstring\\
xparse\\
geometry\\

@@

\subsection{Sql}
Example:\\[3pt]
\sql{SELECT * FROM test;}\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\sql[options][textForPage]{queryForOverlay}| \\
\textbf{Note:} if \verb|textForPage| is omitted the \verb|queryForOverlay| is used as text for the page.\\[8pt]

@@

\subsection{DataText}
Produce text from sql-statements.\\[3pt]
Example:\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\
The table ``test'' contains the following tuples: \dataText{SELECT * FROM test;}.\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\dataText[options]{query}| \\[8pt]

@@

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{PDBF}
\usepackage{wrapfig}
\usepackage[hidelinks]{hyperref}
\usepackage[a4paper,vmargin={20mm,40mm},hmargin={20mm,20mm}]{geometry}

@@

\section{Requirements}
These \LaTeX\relax packages are required for PDBF documents:\\
zref\\
xcolor\\
graphicx\\
xstring\\
xparse\\
geometry\\
array\\

@@

\subsection{SQL}
Clickable SQL-statements\\[3pt]
Example:\\[3pt]
\sql{SELECT * FROM test;}\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\sql[options][textForPage]{queryForOverlay}| \\
\textbf{Note:} if \verb|textForPage| is omitted the \verb|queryForOverlay| is used as text for the page.\\[8pt]

@@

\subsection{DataText}
Write text that is the result of a SQL-statement.\\[3pt]
Example:\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\
The table ``test'' contains the following tuples: \dataText{SELECT * FROM test;}.\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\dataText[options]{query}| \\[8pt]

@@

\subsection{DataTable}
Write a \LaTeX\space table that is the result of a SQL-statement.\\[3pt]
Example:\\[3pt]
\dataTable{SELECT * FROM test;}\\[5pt]
%
\noindent Macros: \\[3pt]
\verb|\dataTable[options]{query}| \\[8pt]

\option
{verticalLines}
{Specifies the vertical lines for the table.}
{\texttt{a} for all, \texttt{i} for inner, \texttt{o} for outer, \texttt{n} for none, or you can use the default tabular syntax (e.g. \texttt{|l|c|r|})}
{\texttt{a}}

\option
{horizontalLinesHeader}
{Specifies the horizontal lines for the table header.}
{\texttt{a} for all, \texttt{i} for inner, \texttt{o} for outer, \texttt{n} for none, or you can specify a custom pattern that is repeatedly applied with the following format: h means line, b means no line, the space character delimits format specifiers. E.g. ``hh b'' means: double line followed by no line followed by double line followed by no line ... and so on}
{\texttt{a}}

\option
{horizontalLinesBody}
{Specifies the horizontal lines for the table body, excluding the border above the first tuple, which is controlled by horizontalLinesHeader.}
{\texttt{a} for all, \texttt{i} for inner, \texttt{o} for outer, \texttt{n} for none, or you can specify a custom pattern that is repeatedly applied with the following format: h means line, b means no line, the space character delimits format specifiers. E.g. ``hh b'' means: double line followed by no line followed by double line followed by no line ... and so on}
{\texttt{a}}

### 2015-07-22 minimal.tex
implemented dataTables and fixed some minor bugs

\documentclass[10pt]{minimal}
\usepackage{PDBF}
\usepackage[a4paper]{geometry}

@@

\begin{document}
\noindent
\sql{SELECT * FROM test;}\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\[3pt]
The following points are linked to the chart below: \dataText[linkTo=testname, linkSelector=2, linkLabel=Value at 2]{SELECT * FROM test WHERE a=2;}, \dataText[linkTo=testname, linkSelector=3, linkLabel=Value at 3]{SELECT * FROM test WHERE a=3;}.\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=line, name=testname]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=bar]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=signatureplot]{SELECT b FROM test;}\\[3pt]
\multiplotChart[width=\textwidth, height=0.9\textwidth, xCount=2, yCount=2, yValues={["b", "b*2"]}, xValues={["a > 2", "a <= 2"]}, yFirst]{SELECT a,? FROM test WHERE ?;}\\[3pt]
\pivotTable[width=\textwidth, height=0.5\textwidth, rows={["a"]}, aggregationattribute=b]{SELECT * FROM test;}
\end{document}

>>>>

\documentclass[10pt]{article}
\usepackage{PDBF}
\usepackage[a4paper]{geometry}

@@

\begin{document}
\noindent
\sql{SELECT * FROM test;}\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\[3pt]
The following points are linked to the chart below: \dataText[linkTo=testname, linkSelector=2, linkLabel=Value at 2]{SELECT * FROM test WHERE a=2;}, \dataText[linkTo=testname, linkSelector=3, linkLabel=Value at 3]{SELECT * FROM test WHERE a=3;}.\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=line, name=testname]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=bar]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=signatureplot]{SELECT b FROM test;}\\[3pt]
\multiplotChart[width=\textwidth, height=0.9\textwidth, xCount=2, yCount=2, yValues={["b", "b*2"]}, xValues={["a > 2", "a <= 2"]}, yFirst]{SELECT a,? FROM test WHERE ?;}\\[3pt]
\pivotTable[width=\textwidth, height=0.5\textwidth, rows={["a"]}, aggregationattribute=b]{SELECT * FROM test;}\\[3pt]
\dataTable[verticalLines=i, horizontalLinesHeader=b hh, horizontalLinesBody=i]{SELECT * FROM test;}\\[3pt]
\end{document}
